Stat 400 Project

### 2021-12-16 Stat 400 proj.Rmd
Wrote about the simulator function
Readme updated

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#testing github
library(tidyverse)
library(ggplot2)
library(boot)
```

@@

```{r}
simulator22 <- function(days, num_subjects, x_dim, y_dim, I_0, inf_dist){
  initial_data <- starting_vals(num_subjects = num_subjects, x_dim=x_dim, y_dim=y_dim, I_0=I_0)
  end_day <- list()
  num_cases <- rep(NA, days)
  num_cases <- c(I_0, num_cases)
  num_new_cases <- rep(NA, days)

@@

    }
  }
  return(end_day)
}
days <- simulator22(20, 5, 1, 1, 1, 0.2)
days

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(boot)
```

@@

```{r}
simulator22 <- function(days, num_subjects, x_dim, y_dim, I_0, inf_dist, prop_vac){
  initial_data <- starting_vals(num_subjects = num_subjects, x_dim=x_dim, y_dim=y_dim, I_0=I_0, prop_vac = prop_vac)
  end_day <- list()
  num_cases <- rep(NA, days)
  num_cases <- c(I_0, num_cases)
  num_new_cases <- rep(NA, days)

@@

    }
  }
  return(end_day)
}
days <- simulator22(20, 5, 1, 1, 1, 0.2, 0)
days
